### 2018-03-16 2017/NACO/NACO-16-0035_3.tex

% !!!IMPORTANT NOTE: Please read carefully all information including those preceded by % sign
%Before you compile the tex file please download the class file AIMS.cls from the following URL link to the
%local folder where your tex file resides. http://aimsciences.org/journals/tex-sample/AIMS.cls.
\documentclass{aims}
\usepackage{amsmath}
  \usepackage{paralist}
  \usepackage{graphics} %% add this and next lines if pictures should be in esp format
  \usepackage{epsfig} %For pictures: screened artwork should be set up with an 85 or 100 line screen
\usepackage{graphicx}  \usepackage{epstopdf}%This is to transfer .eps figure to .pdf figure; please compile your paper using PDFLeTex or PDFTeXify.
 \usepackage[colorlinks=true]{hyperref}
   % Warning: when you first run your tex file, some errors might occur,
   % please just press enter key to end the compilation process, then it will be fine if you run your tex file again.
   % Note that it is highly recommended by AIMS to use this package.
\hypersetup{urlcolor=blue, citecolor=red}
%\usepackage{hyperref}

\usepackage[utf8]{inputenc}

  \textheight=8.2 true in
   \textwidth=5.0 true in
    \topmargin 30pt
     \setcounter{page}{1}

% The next 5 line will be entered by an editorial staff.
\def\currentvolume{X}
 \def\currentissue{X}
  \def\currentyear{200X}
   \def\currentmonth{XX}
    \def\ppages{X--XX}
     \def\DOI{10.3934/xx.xx.xx.xx}

 % Please minimize the usage of "newtheorem", "newcommand", and use
 % equation numbers only situation when they provide essential convenience
 % Try to avoid defining your own macros

@@

\centerline{\scshape Victor Gergel, Konstantin  Barkalov$^*$ and Alexander Sysoyev}
\medskip
{\footnotesize
 % please put the address of the second  and third author
 \centerline{Lobachevsky State University of Nizhni Novgorod}
   \centerline{23, Gagarin Avenue, Nizhni Novgorod, Russia}
}

@@

% The name of the associate editor will be entered by an editorial staff
% "Communicated by the associate editor name" is not needed for special issue.
 \centerline{(Communicated by the associate editor name)}

@@

The list provided above is certainly not exhaustive – additional information on the

@@

\par
The architecture of the Globalizer system is presented in Figure \ref{fig:globalizerScheme}.
The system components are:
\begin{itemize}
  \item Block 0 consists of the procedures for computing the function values
  (criteria and constraints) of the optimization problem being solved; it is an external
  block with a predefined interface with respect to the Globalizer system and is provided by the user.
  \item Blocks 1-4 form the optimization subsystem and solve the global optimization
  problems (Block 1), nonlinear programming ones (Block 2), multicriterial optimization problems
  (Block 3), and general decision making problems (Block 4). The interaction between these
  components is organized in a hierarchical order --- the decision making problems are
  solved using the multicriterial optimization block, which, in turn, uses the nonlinear programming block, and so on.
  \item Block 5 is a subsystem for accumulating and processing the search information; it is one of the main subsystems – the size of search information may appear to be quite large and the efficiency of the global optimization methods depends on how completely the available search data are utilized.
  \item Block 6 contains the dimensionality reduction procedures based on the Peano space-filling curves; the reduced (one-dimensional) optimization problems are solved by the optimization blocks. This block also provides the interaction between the optimization blocks and the multidimensional optimization problem being solved.
  \item Block 7 provides tuning the parallel computation schemes in the Globalizer system subject to the employed computational system architecture (the number of the computational cores, the availability of shared and/or distributed memory, the availability of computational accelerators, etc.) and the applied global optimization methods.
  \item Block 8 is responsible for managing the parallel processes when performing the global optimization (determining the optimal configuration of parallel processes, distributing the processes between the computational units, balancing the computational loads, etc.).
  \item Block 9 is a managing subsystem, which controls the parallel computations when solving the global optimization problems.
  \item Block 10 provides the dialog interaction with the users for stating the optimization problem, adjusting the system parameters (if necessary), and visualizing and presenting the global optimization results.
  \item Block 11 is a set of tools for visualizing and presenting the global optimization results; the availability of the tools for visual demonstration of the computational results enables the user to perform an efficient control over the global optimization process.
\end{itemize}
\par
The Globalizer system comes in two different versions:
\begin{itemize}
  \item Globalizer Pro is a research version for making various large-scale numerical experiments on the high-performance computational systems to investigate the new parallel global optimization methods being developed.
  \item Globalizer Lite is a limited version for solving the global optimization problems with a medium complexity level, and is accessible for free usage.
\end{itemize}

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system – CentOS 6.4, the
supercomputer management system – SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 2.2 GHz processors with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores. In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (in total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function values was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.

@@

\begin{thebibliography}{10}

\bibitem{barkalovGergel2014}
\newblock K. Barkalov and V. Gergel,
\newblock Multilevel scheme of dimensionality reduction for parallel global search algorithms,
\newblock in \emph{Proceedings of the 1st International Conference on
  Engineering and Applied Sciences Optimization}, (2014), 2111--2124.

\bibitem{barkalovGergel2015}[10.1007/s10898-016-0411-y]
\newblock K. Barkalov and V. Gergel,
\newblock Parallel global optimization on GPU,
\newblock \emph{J. Glob. Optim.}, \textbf{66(1)} (2016), 3--20.

\bibitem{barkalovGergelLebedev2015}[10.1007/978-3-319-21909-7_31]
\newblock K. Barkalov, V. Gergel and I. Lebedev,
\newblock Use of Xeon Phi coprocessor for solving global optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 307--318.

\bibitem{barkalovGergelLebedevSysoev2015}
\newblock K. Barkalov, V. Gergel, I. Lebedev, A. Sysoev, %http://ceur-ws.org/Vol-1482/
\newblock Solving the global optimization problems on heterogeneous cluster systems,
\newblock in \emph{CEUR Workshop Proceedings}, \textbf{1482} (2015), 411--419.
%\newblock (In Russian).

\bibitem{Barkalov2013}[10.1007/978-3-642-39958-9_14]
\newblock K. Barkalov, A. Polovinkin, I. Meyerov, S. Sidorov, N. Zolotykh,
\newblock SVM regression parameters optimization using parallel global search algorithm,
\newblock \emph{LNCS}, \textbf{7979} (2013), 154--166.

\bibitem{bussieckMeeraus2004}[10.1007/978-1-4613-0215-5_8]
\newblock M. R. Bussieck and A. Meeraus,
\newblock General algebraic modeling system (GAMS), in \emph{Modeling Languages in Mathematical Optimization} (ed. J. Kallrath),
\newblock Springer (2004), 137--157.

\bibitem{censorZeniosParGO}
\newblock Y. Censor and S. A. Zenios,
\newblock \emph{Parallel optimization: theory, algorithms, and applications},
\newblock Oxford University Press (1998).

\bibitem{ciegisHentyParGO}[10.1007/978-0-387-09707-7]
\newblock R. \v Ciegis, D. Henty, B. K\aa gstr\"om and J. \v Zilinskas,
\newblock \emph{Parallel scientific computing and optimization: advances and applications},
\newblock Springer (2009).

\bibitem{iosoDescription}
\newblock I. N. Egorov, G. V. Kretinin, I. A. Leshchenko and S. V. Kuptzov,
\newblock IOSO optimization toolkit --- novel software to create better design,
\newblock in \emph{9th AIAA/ISSMO Symposium on Multidisciplinary Analysis and Optimization}, 2002.
\newblock Available from \url{http://www.iosotech.com/text/2002\_4329.pdf}.

\bibitem{Famularo1999}[10.1016/S0005-1098(99)00058-8]
\newblock D. Famularo, P. Pugliese and Y. D. Sergeyev,
\newblock A global optimization technique for checking parametric robustness,
\newblock \emph{Automatica}, \textbf{35} (1999), 1605--1611.

\bibitem{fasanoPinter2013}[10.1007/978-1-4614-4469-5]
\newblock G. Fasano and J. D. Pint\'er,
\newblock \emph{Modeling and optimization in space engineering},
\newblock Springer, 2013.

\bibitem{floudasPardalosGOState}[10.1007/978-1-4613-3437-8]
\newblock C. A. Floudas and M. P. Pardalos,
\newblock \emph{State of the art in global optimization: computational methods and applications},
\newblock Kluwer Academic Publishers, Dordrecht (1996).

\bibitem{floudasPardGO}[10.1007/s10898-008-9332-8]
\newblock C. A. Floudas and M. P. Pardalos,
\newblock \emph{Recent advances in global optimization},
\newblock Princeton University Press (2016).

\bibitem{Gablonsky}[10.1023/A:1017930332101]
\newblock J. M. Gablonsky and C. T. Kelley,
\newblock A locally-biased form of the DIRECT algorithm,
\newblock \emph{J. Glob. Optim.}, \textbf{21(1)} (2001), 27--37.

\bibitem{gavianoKvasovLeraSergeev2003}[10.1145/962437.962444]
\newblock M. Gaviano, D. E. Kvasov, D. Lera and Y. D. Sergeev,
\newblock Software for generation of classes of test functions with known local and global minima for global optimization,
\newblock \emph{ACM Trans. Math. Software}, \textbf{29(4)} (2003), 469--480.

\bibitem{gergelLebedev2015}[10.1016/j.procs.2015.11.008]
\newblock V. Gergel and I. Lebedev,
\newblock Heterogeneous parallel computations for solving global optimization problems,
\newblock \emph{Procedia Comput. Sci.}, \textbf{66} (2015), 53--62.

\bibitem{gergel1993}
\newblock V. Gergel,
\newblock A software system for multi-extremal optimization,
\newblock \emph{Eur. J. Oper. Res.}, \textbf{65(3)} (1993), 305--313.

\bibitem{gergel1996}
\newblock V. Gergel,
\newblock A method for using derivatives in the minimization of multiextremum functions,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{36(6)} (1996), 729--742.

\bibitem{gergel1997}[10.1023/A:1008290629896]
\newblock V. Gergel,
\newblock A global optimization algorithm for multivariate functions with Lipschitzian first derivatives,
\newblock \emph{J. Glob. Optim.}, \textbf{10(3)} (1997), 257--281.

\bibitem{gergel2013}[doi:10.1016/j.procs.2013.05.164]
\newblock V. Gergel, et al.,
\newblock High performance computing in biomedical applications,
\newblock \emph{Procedia Computer Science}, \textbf{18} (2013), 10--19.

\bibitem{gergel2015}[10.15866/ireaco.v8i1.4935]
\newblock V. Gergel, et al.,
\newblock Recognition of surface defects of cold-rolling sheets based on method of localities,
\newblock \emph{International Review of Automatic Control }, \textbf{8(1)} (2015), 51--55.

\bibitem{gergelSidorov2015}[10.1007/978-3-319-21909-7_49]
\newblock V. Gergel and S. Sidorov,
\newblock A two-level parallel global search algorithm for solving computationally intensive multi-extremal optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 505--515.

\bibitem{grishaginStrongin1984}
\newblock V. A. Grishagin and R. G. Strongin,
\newblock Optimization of multi-extremal functions subject to monotonically unimodal constraints,
\newblock \emph{Engineering Cybernetics}, \textbf{5} (1984), 117--122.

\bibitem{holmstromEdvall2004}[10.1007/978-1-4613-0215-5_19]
\newblock K. Holmström and M. M. Edvall,
\newblock The TOMLAB optimization environment,
\newblock \emph{Modeling Languages in Mathematical Optimization},
\newblock 369--376, Springer (2004).

\bibitem{horstTuyGO}[10.1007/978-3-662-03199-5]
\newblock R. Horst and H. Tuy,
\newblock \emph{Global optimization: deterministic approaches},
\newblock Springer-Verlag, Berlin (1990).

\bibitem{Jones}[10.1007/BF00941892]
\newblock D. R. Jones, C. D. Perttunen and B. E. Stuckman,
\newblock Lipschitzian optimization without the Lipschitz constant,
\newblock \emph{J. Optim. Theory Appl.}, \textbf{79(1)} (1993), 157--181.

\bibitem{kearfott2009}[10.1080/10556780802614051]
\newblock R. B. Kearfott,
\newblock GlobSol user guide,
\newblock \emph{Optim. Methods Softw.}, \textbf{24} (2009), 687--708.

\bibitem{Kvasov2015}[10.1016/j.advengsoft.2014.09.014]
\newblock D. E. Kvasov and Y. D. Sergeyev,
\newblock Deterministic approaches for solving practical black-box global optimization problems,
\newblock \emph{Adv. Eng. Softw.}, \textbf{80} (2015), 58--66.

\bibitem{Menniti}[10.1016/j.epsr.2007.10.009]
\newblock D. E. Kvasov, D. Menniti, A. Pinnarelli, Y. D. Sergeyev and N. Sorrentino,
\newblock Tuning fuzzy power-system stabilizers in multi-machine systems by global optimization algorithms based on efficient domain partitions,
\newblock \emph{Electric Power Systems Research}, \textbf{78(7)} (2008), 1217--1229.

\bibitem{Pizzuti}[10.1007/s00211-002-0419-8]
\newblock D. E. Kvasov, C. Pizzuti and Y. D. Sergeyev,
\newblock Local tuning and partition strategies for diagonal GO methods,
\newblock \emph{Numerische Mathematik}, \textbf{94(1)} (2003), 93--106.

\bibitem{liberti2009}[10.1007/0-387-30528-9_8]
\newblock L. Liberti,
\newblock Writing global optimization software,
\newblock in \emph{Nonconvex Optimization and Its Applications }, \textbf{84}, 211--262,
\newblock Springer (2006).

\bibitem{linSchrage2009}[10.1080/10556780902753221]
\newblock Y. Lin and L. Schrage,
\newblock The global solver in the LINDO API,
\newblock \emph{Optim. Methods Softw.}, \textbf{24(4-5)} (2009), 657--668.

\bibitem{locatelliSchoenGO}[10.1137/1.9781611972672]
\newblock M. Locatelli and F. Schoen,
\newblock \emph{Global optimization: theory, algorithms and applications},
\newblock SIAM (2013).

\bibitem{luqueAlbaGA}[10.1007/978-3-642-22084-5]
\newblock G. Luque and E. Alba,
\newblock \emph{Parallel genetic algorithms. Theory and real world applications},
\newblock Springer-Verlag, Berlin (2011).

\bibitem{mongeauKarsentyRouze2000}[10.1080/10556780008805783]
\newblock M. Mongeau, H. Karsenty, V. Rouzé and J. B. Hiriart-Urruty,
\newblock Comparison of public-domain software for black box global optimization,
\newblock \emph{Optim. Methods Softw.}, \textbf{13} (2000), 203--226.

\bibitem{mullen2014}[10.18637/jss.v060.i06]
\newblock K. M. Mullen,
\newblock Continuous global optimization in R,
\newblock \emph{J. Stat. Softw.}, \textbf{60(6)} (2014).

\bibitem{pardalosZhigljavskyZilinskas2016}[10.1007/978-3-319-29975-4]
\newblock M. P. Pardalos, A. A. Zhigljavsky and J. \v Zilinskas,
\newblock \emph{Advances in stochastic and deterministic global optimization},
\newblock Springer (2016).

\bibitem{pinterGO}[10.1007/978-1-4757-2502-5]
\newblock J. D. Pint\'er,
\newblock \emph{Global optimization in action (Continuous and Lipschitz optimization: algorithms, implementations and applications)},
\newblock Kluwer Academic Publishers, Dordrecht (1996).

\bibitem{pinter2009}
\newblock J. D. Pint\'er,
\newblock Software development for global optimization,
\newblock \emph{Lectures on Global Optimization. Fields Institute Communications}, \textbf{55} (2009), 183--204.

\bibitem{riosSahinidis2013}[10.1007/s10898-012-9951-y]
\newblock L. M. Rios and N. V. Sahinidis,
\newblock Derivative-free optimization: a review of algorithms and comparison of software implementations,
\newblock \emph{J. Glob. Optim.}, \textbf{56} (2013), 1247--1293.

\bibitem{sahinidis1996}[10.1007/BF00138693]
\newblock N. V. Sahinidis,
\newblock BARON: A general purpose global optimization software package,
\newblock \emph{J. Glob. Optim.}, \textbf{8} (1996), 201--205.

\bibitem{sergeyev1995}[10.1137/0805041]
\newblock Y. D. Sergeyev,
\newblock An information global optimization algorithm with local tuning,
\newblock \emph{SIAM J. Optim.}, \textbf{5(4)} (1995), 858--870.

\bibitem{sergeyev1999}
\newblock Y. D. Sergeyev,
\newblock Multidimensional global optimization using the first derivatives,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{39(5)} (1999), 743--752.

>>>>

% !!!IMPORTANT NOTE: Please read carefully all information including those preceded by % sign
%Before you compile the tex file please download the class file AIMS.cls from the following URL link to the
%local folder where your tex file resides. http://aimsciences.org/journals/tex-sample/AIMS.cls.
\documentclass{naco}
\usepackage{amsmath}
  \usepackage{paralist}
  \usepackage{graphics} %% add this and next lines if pictures should be in esp format
  \usepackage{epsfig} %For pictures: screened artwork should be set up with an 85 or 100 line screen
\usepackage{graphicx}  \usepackage{epstopdf}%This is to transfer .eps figure to .pdf figure; please compile your paper using PDFLeTex or PDFTeXify.
 \usepackage[colorlinks=true]{hyperref}
   % Warning: when you first run your tex file, some errors might occur,
   % please just press enter key to end the compilation process, then it will be fine if you run your tex file again.
   % Note that it is highly recommended by AIMS to use this package.
\hypersetup{urlcolor=blue, citecolor=red}
%\usepackage{hyperref}

%\usepackage[utf8]{inputenc}

  \textheight=8.2 true in
   \textwidth=5.0 true in
    \topmargin 30pt
     \setcounter{page}{47}

% The next 5 line will be entered by an editorial staff.
\def\currentvolume{8}
 \def\currentissue{1}
  \def\currentyear{2018}
   \def\currentmonth{March}
    \def\ppages{47--62}
     \def\DOI{10.3934/naco.2018003}
 % Please minimize the usage of "newtheorem", "newcommand", and use
 % equation numbers only situation when they provide essential convenience
 % Try to avoid defining your own macros

@@

\centerline{\scshape Victor Gergel, Konstantin  Barkalov$^*$  }
\centerline{\scshape and Alexander Sysoyev}
\medskip
{\footnotesize
 % please put the address of the second  and third author
 \centerline{Lobachevsky State University of Nizhni Novgorod}
   \centerline{23, Gagarin Avenue, Nizhni Novgorod, Russia}
}

@@

% The name of the associate editor will be entered by an editorial staff
% "Communicated by the associate editor name" is not needed for special issue.
 \centerline{(Communicated by Yaroslav Sergeyev)}

@@

The list provided above is certainly not exhaustive --- additional information on the

@@

\par
The architecture of the Globalizer system is presented in Figure \ref{fig:globalizerScheme}.
The system components are:
\begin{itemize}
  \item Block 0 consists of the procedures for computing the function values
  (criteria and constraints) of the optimization problem being solved; it is an external
  block with a predefined interface with respect to the Globalizer system and is provided by the user.
  \item Blocks 1-4 form the optimization subsystem and solve the global optimization
  problems (Block 1), nonlinear programming ones (Block 2), multicriterial optimization problems
  (Block 3), and general decision making problems (Block 4). The interaction between these
  components is organized in a hierarchical order --- the decision making problems are
  solved using the multicriterial optimization block, which, in turn, uses the nonlinear programming block, and so on.
  \item Block 5 is a subsystem for accumulating and processing the search information; it is one of the main subsystems --- the size of search information may appear to be quite large and the efficiency of the global optimization methods depends on how completely the available search data are utilized.
  \item Block 6 contains the dimensionality reduction procedures based on the Peano space-filling curves; the reduced (one-dimensional) optimization problems are solved by the optimization blocks. This block also provides the interaction between the optimization blocks and the multidimensional optimization problem being solved.
  \item Block 7 provides tuning the parallel computation schemes in the Globalizer system subject to the employed computational system architecture (the number of the computational cores, the availability of shared and/or distributed memory, the availability of computational accelerators, etc.) and the applied global optimization methods.
  \item Block 8 is responsible for managing the parallel processes when performing the global optimization (determining the optimal configuration of parallel processes, distributing the processes between the computational units, balancing the computational loads, etc.).
  \item Block 9 is a managing subsystem, which controls the parallel computations when solving the global optimization problems.
  \item Block 10 provides the dialog interaction with the users for stating the optimization problem, adjusting the system parameters (if necessary), and visualizing and presenting the global optimization results.
  \item Block 11 is a set of tools for visualizing and presenting the global optimization results; the availability of the tools for visual demonstration of the computational results enables the user to perform an efficient control over the global optimization process.
\end{itemize}
\par
The Globalizer system comes in two different versions:
\begin{itemize}
  \item Globalizer Pro is a research version for making various large-scale numerical experiments on the high-performance computational systems to investigate the new parallel global optimization methods being developed.
  \item Globalizer Lite is a limited version for solving the global optimization problems with a medium complexity level, and is accessible for free usage.
\end{itemize}

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system --- CentOS 6.4, the
supercomputer management system --- SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 2.2 GHz processors with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores. In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (in total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function values was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.

@@

\begin{thebibliography}{99}

\bibitem{barkalovGergel2014}
\newblock K. Barkalov and V. Gergel,
\newblock \emph{\emph{Multilevel scheme of dimensionality reduction for parallel global search algorithms}},
\newblock in \emph{Proceedings of the 1st International Conference on Engineering and Applied Sciences Optimization}, (2014), 2111--2124.

\bibitem{barkalovGergel2015} (MR3539505) [10.1007/s10898-016-0411-y]
\newblock K. Barkalov and V. Gergel,
\newblock \emph{\emph{Parallel global optimization on GPU}},
\newblock \emph{J. Glob. Optim.}, \textbf{66} (2016), 3--20.

\bibitem{barkalovGergelLebedev2015} [10.1007/978-3-319-21909-7_31]
\newblock K. Barkalov, V. Gergel and I. Lebedev,
\newblock \emph{\emph{Use of Xeon Phi coprocessor for solving global optimization problems}},
\newblock \emph{LNCS}, \textbf{9251} (2015), 307--318.

\bibitem{barkalovGergelLebedevSysoev2015}
\newblock K. Barkalov, V. Gergel, I. Lebedev and A. Sysoev,
\newblock \emph{\emph{Solving the global optimization problems on heterogeneous cluster systems}},
\newblock in \emph{CEUR Workshop Proceedings}, \textbf{1482} (2015), 411--419.

\bibitem{Barkalov2013} [10.1007/978-3-642-39958-9_14]
\newblock K. Barkalov, A. Polovinkin, I. Meyerov, S. Sidorov and N. Zolotykh,
\newblock \emph{\emph{SVM regression parameters optimization using parallel global search algorithm}},
\newblock \emph{LNCS}, \textbf{7979} (2013), 154--166.

\bibitem{bussieckMeeraus2004} (MR3618583) [10.1007/978-1-4613-0215-5_8]
\newblock M. R. Bussieck and A. Meeraus,
\newblock \emph{\emph{General algebraic modeling system (GAMS)}},
\newblock in \emph{Modeling Languages in Mathematical Optimization} (ed. J. Kallrath), Springer, (2004), 137--157.

\bibitem{censorZeniosParGO} (MR1486040)
\newblock Y. Censor and S. A. Zenios,
\newblock \emph{Parallel Optimization: Theory, Algorithms, and Applications},
\newblock Oxford University Press, 1998.

\bibitem{ciegisHentyParGO} (MR2499546) [10.1007/978-0-387-09707-7]
\newblock R. \v Ciegis, D. Henty, B. K\aa gstr\"om and J. \v Zilinskas,
\newblock \emph{Parallel Scientific Computing and Optimization: Advances and Applications},
\newblock Springer, 2009.

\bibitem{iosoDescription}
\newblock I. N. Egorov, G. V. Kretinin, I. A. Leshchenko and S. V. Kuptzov,
\newblock \emph{\emph{IOSO optimization toolkit --- novel software to create better design}},
\newblock in \emph{9th AIAA/ISSMO Symposium on Multidisciplinary Analysis and Optimization}, 2002. Available from \url{http://www.iosotech.com/text/2002\_4329.pdf}.

\bibitem{Famularo1999} (MR1827451) [10.1016/S0005-1098(99)00058-8]
\newblock D. Famularo, P. Pugliese and Y. D. Sergeyev,
\newblock \emph{\emph{A global optimization technique for checking parametric robustness}},
\newblock \emph{Automatica}, \textbf{35} (1999), 1605--1611.

\bibitem{fasanoPinter2013} (MR3013800) [10.1007/978-1-4614-4469-5]
\newblock G. Fasano and J. D. Pint\'er,
\newblock \emph{Modeling and Optimization in Space Engineering},
\newblock Springer, 2013.

\bibitem{floudasPardalosGOState} (MR1390521) [10.1007/978-1-4613-3437-8]
\newblock C. A. Floudas and M. P. Pardalos,
\newblock \emph{State of the Art in Global Optimization: Computational Methods and Applications},
\newblock Kluwer Academic Publishers, Dordrecht, 1996.

\bibitem{floudasPardGO} (MR1147432) [10.1007/s10898-008-9332-8]
\newblock C. A. Floudas and M. P. Pardalos,
\newblock \emph{Recent Advances in Global Optimization},
\newblock Princeton University Press, 2016.

\bibitem{Gablonsky} (MR1856800) [10.1023/A:1017930332101]
\newblock J. M. Gablonsky and C. T. Kelley,
\newblock \emph{\emph{A locally-biased form of the DIRECT algorithm}},
\newblock \emph{J. Glob. Optim.}, \textbf{21} (2001), 27--37.

\bibitem{gavianoKvasovLeraSergeev2003} (MR2077342) [10.1145/962437.962444]
\newblock M. Gaviano, D. E. Kvasov, D. Lera and Y. D. Sergeev,
\newblock \emph{\emph{Software for generation of classes of test functions with known local and global minima for global optimization}},
\newblock \emph{ACM Trans. Math. Software}, \textbf{29} (2003), 469--480.

\bibitem{gergelLebedev2015} [10.1016/j.procs.2015.11.008]
\newblock V. Gergel and I. Lebedev,
\newblock \emph{\emph{Heterogeneous parallel computations for solving global optimization problems}},
\newblock \emph{Procedia Comput. Sci.}, \textbf{66} (2015), 53--62.

\bibitem{gergel1993}
\newblock V. Gergel,
\newblock \emph{\emph{A software system for multi-extremal optimization}},
\newblock \emph{Eur. J. Oper. Res.}, \textbf{65} (1993), 305--313.

\bibitem{gergel1996} (MR1399766)
\newblock V. Gergel,
\newblock \emph{\emph{A method for using derivatives in the minimization of multiextremum functions}},
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{36} (1996), 729--742.

\bibitem{gergel1997} (MR1443089) [10.1023/A:1008290629896]
\newblock V. Gergel,
\newblock \emph{\emph{A global optimization algorithm for multivariate functions with Lipschitzian first derivatives}},
\newblock \emph{J. Glob. Optim.}, \textbf{10} (1997), 257--281.

\bibitem{gergel2013} [doi:10.1016/j.procs.2013.05.164]
\newblock V. Gergel, et al.,
\newblock \emph{\emph{High performance computing in biomedical applications}},
\newblock \emph{Procedia Computer Science}, \textbf{18} (2013), 10--19.

\bibitem{gergel2015} [10.15866/ireaco.v8i1.4935]
\newblock V. Gergel, et al.,
\newblock \emph{\emph{Recognition of surface defects of cold-rolling sheets based on method of localities}},
\newblock \emph{International Review of Automatic Control, } \textbf{8} (2015), 51--55.

\bibitem{gergelSidorov2015} [10.1007/978-3-319-21909-7_49]
\newblock V. Gergel and S. Sidorov,
\newblock \emph{\emph{A two-level parallel global search algorithm for solving computationally intensive multi-extremal optimization problems}},
\newblock \emph{LNCS}, \textbf{9251} (2015), 505--515.

\bibitem{grishaginStrongin1984} (MR785497)
\newblock V. A. Grishagin and R. G. Strongin,
\newblock \emph{\emph{Optimization of multi-extremal functions subject to monotonically unimodal constraints}},
\newblock \emph{Engineering Cybernetics}, \textbf{5} (1984), 117--122.

\bibitem{holmstromEdvall2004} [10.1007/978-1-4613-0215-5_19]
\newblock K. Holmstrm and M. M. Edvall,
\newblock \emph{\emph{The TOMLAB optimization environment}},
\newblock \emph{Modeling Languages in Mathematical Optimization}, Springer, (2004), 369--376.

\bibitem{horstTuyGO} (MR1102239) [10.1007/978-3-662-03199-5]
\newblock R. Horst and H. Tuy,
\newblock \emph{Global Optimization: Deterministic Approaches},
\newblock Springer-Verlag, Berlin, 1990.

\bibitem{Jones} (MR1246501) [10.1007/BF00941892]
\newblock D. R. Jones, C. D. Perttunen and B. E. Stuckman,
\newblock \emph{\emph{Lipschitzian optimization without the Lipschitz constant}},
\newblock \emph{J. Optim. Theory Appl.}, \textbf{79} (1993), 157--181.

\bibitem{kearfott2009} (MR2554906) [10.1080/10556780802614051]
\newblock R. B. Kearfott,
\newblock \emph{\emph{GlobSol user guide}},
\newblock \emph{Optim. Methods Softw.}, \textbf{24} (2009), 687--708.

\bibitem{Kvasov2015} (MR3585540) [10.1016/j.advengsoft.2014.09.014]
\newblock D. E. Kvasov and Y. D. Sergeyev,
\newblock \emph{\emph{Deterministic approaches for solving practical black-box global optimization problems}},
\newblock \emph{Adv. Eng. Softw.}, \textbf{80} (2015), 58--66.

\bibitem{Menniti} [10.1016/j.epsr.2007.10.009]
\newblock D. E. Kvasov, D. Menniti, A. Pinnarelli, Y. D. Sergeyev and N. Sorrentino,
\newblock \emph{\emph{Tuning fuzzy power-system stabilizers in multi-machine systems by global optimization algorithms based on
 efficient domain partitions}},
\newblock \emph{Electric Power Systems Research}, \textbf{78} (2008), 1217--1229.

\bibitem{Pizzuti} (MR1971214) [10.1007/s00211-002-0419-8]
\newblock D. E. Kvasov, C. Pizzuti and Y. D. Sergeyev,
\newblock \emph{\emph{Local tuning and partition strategies for diagonal GO methods}},
\newblock \emph{Numerische Mathematik}, \textbf{94} (2003), 93--106.

\bibitem{liberti2009} (MR2206955) [10.1007/0-387-30528-9_8]
\newblock L. Liberti,
\newblock \emph{\emph{Writing global optimization software}},
\newblock in \emph{Nonconvex Optimization and Its Applications}, Springer, \textbf{84} (2006), 211--262.

\bibitem{linSchrage2009} (MR2554904) [10.1080/10556780902753221]
\newblock Y. Lin and L. Schrage,
\newblock \emph{\emph{The global solver in the LINDO API}},
\newblock \emph{Optim. Methods Softw.}, \textbf{24} (2009), 657--668.

\bibitem{locatelliSchoenGO} (MR3136805) [10.1137/1.9781611972672]
\newblock M. Locatelli and F. Schoen,
\newblock \emph{Global Optimization: Theory, Algorithms and Applications},
\newblock SIAM, 2013.

\bibitem{luqueAlbaGA} (MR2808873) [10.1007/978-3-642-22084-5]
\newblock G. Luque and E. Alba,
\newblock \emph{Parallel Genetic Algorithms. Theory and Real World Applications},
\newblock Springer-Verlag, Berlin, 2011.

\bibitem{mongeauKarsentyRouze2000} (MR1785196) [10.1080/10556780008805783]
\newblock M. Mongeau, H. Karsenty, V. Rouz$\acute{e}$ and J. B. Hiriart-Urruty,
\newblock \emph{\emph{Comparison of public-domain software for black box global optimization}},
\newblock \emph{Optim. Methods Softw.}, \textbf{13} (2000), 203--226.

\bibitem{mullen2014} [10.18637/jss.v060.i06]
\newblock K. M. Mullen,
\newblock \emph{\emph{Continuous global optimization in R}},
\newblock \emph{J. Stat. Softw.}, \textbf{60} (2014).

\bibitem{pardalosZhigljavskyZilinskas2016} (MR2361744) [10.1007/978-3-319-29975-4]
\newblock M. P. Pardalos, A. A. Zhigljavsky and J. \v Zilinskas,
\newblock \emph{Advances in Stochastic and Deterministic Global Optimization},
\newblock Springer, 2016.

\bibitem{pinterGO} (MR1374104) [10.1007/978-1-4757-2502-5]
\newblock J. D. Pint\'er,
\newblock \emph{Global Optimization in Action (Continuous and Lipschitz Optimization: Algorithms, Implementations and Applications)},
\newblock Kluwer Academic Publishers, Dordrecht, 1996.

\bibitem{pinter2009} (MR2528693)
\newblock J. D. Pint\'er,
\newblock \emph{\emph{Software development for global optimization}},
\newblock \emph{Lectures on Global Optimization. Fields Institute Communications}, \textbf{55} (2009), 183--204.
